---
title: "FNIH REPORT (ID7 and ID8)"
author: "Yongfang Lu (Modified by Souvik)"
date: "12/08/2022"
output:
  word_document:
    fig_width: 12
    fig_height: 8
    fig_caption: yes
    highlight: pygments
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}

library(knitr)
knitr::opts_chunk$set(echo=FALSE, cache=FALSE, eval=TRUE, warning=FALSE, message=FALSE,  fig.align = "center")

```


# Further formating is needed after kint the docuemnt
# 1: replace ** with whitespace
# 2: merge row of "Candidate Biomarker classification at the optimal cut-point"
# 3: merge row of "Performance Parameters at the optimal cut-point"

```{r loading R packages and source code , echo=FALSE}

rm(list=ls())
#S:\Clients\FNIH\R\Development\Code
setwd("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Code")
DIR_FILES <- "C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Raw_Data\\"
library(openxlsx)
library(readxl)
library(stringr)
library(cutpointr)
library(dplyr)
library(pROC)
library(ggplot2)
List<-c("SUBJID","ageyrs","platelet","Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis","NASH","NAS","At_Risk_NASH","dm2")
List_Endpoint<-List[-c(1:3)]
Def_Endpoint<-read.csv("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\FNIH_Endpoint_Definition.csv")


source("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Code\\Table_Fun2_Space 220114.R")
source("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Code\\Table_Fun_ComparsionCandiatevsBiomarkers 220114.R")

# #for catalog biomarkers, use following functions 
# source("C:\\Users\\yongfangl\\Desktop\\FNIH\\Development\\Code\\CutpointAnalysis_Catalog.R")
# source("C:\\Users\\yongfangl\\Desktop\\FNIH\\Development\\Code\\Table_Fun2_Space_Catalog.R")
# source("C:\\Users\\yongfangl\\Desktop\\FNIH\\Development\\Code\\Table_Fun_ComparsionCandiatevsBiomarkers_Catalog.R")

```


```{r For loading data, message=FALSE,warning=FALSE, results="markup"}

#####################################################################################
####################### #loading data and data handling ############################
#####################################################################################

Siemens<- read.csv(paste0(DIR_FILES,"Nimble_Siemens_24FEB2021.csv"))
Nordic<-  read.csv(paste0(DIR_FILES,"Nimble_Nordic_16APR2021.csv")) # ELISA
#Nordic<-  read.csv(paste0(DIR_FILES,"\\NIMBLE_Nordic_04NOV2021\\Nimble_Nordic_04NOV2021.csv")) #COMBAS records
Labcorp<- read_excel(paste0(DIR_FILES,"NIMBLE_labcorp_18Mar2021.xls"));Labcorp<-Labcorp[-(7453:7455),];Labcorp$Result<-as.numeric(as.character(Labcorp$RESULT))
MetaDat<- read_excel(paste0(DIR_FILES,"nimble_metadata_28mar21.xlsx"))
CRNDat<- read_excel(paste0(DIR_FILES,"nimble_owl_clinds_7apr21.xlsx"),sheet = "Data")
GenfitDat<- read.csv(paste0(DIR_FILES,"Nimble_Genfit_19072021.csv"))
OWLDat<-read.csv(paste0(DIR_FILES,"NIMBLE_OWLiver Panels_Results.csv"))
FibrometerDat1<-read.csv(paste0(DIR_FILES,"fibrometer_LSM_CAP_Agile_FAST_FMVCTE.csv"))
FibrometerDat2<- read.csv(paste0(DIR_FILES,"fibrometer_results_V3G_NAFLD_CirrhoMeter_p.csv"))

PROC3<-read.csv(paste0(DIR_FILES,"\\NIMBLE_Nordic_04NOV2021\\Nimble_Nordic_Cobas_04NOV2021.csv"))# COMBAS records



#processing data
# why lapcrop list patient names twice, keep one is enough-> YES!!!
PATIENT_NAME<-do.call("rbind",strsplit(Labcorp$`PATIENT NAME`, "        "))
# sum(PATIENT_NAME[,1]==PATIENT_NAME[,2])==nrow(PATIENT_NAME)
# Labcorp$`PATIENT NAME`<-PATIENT_NAME[,1]
# unique(Labcorp$TEST_ORD_NAME) # 7 unque parameters from Labcorp data
# # [1] "Protein, Total"       "Albumin"              "Bilirubin, Total"     "Bilirubin, Direct"    "Alkaline Phosphatase"
# # [6] "AST (SGOT)"           "ALT (SGPT)"
# 
# unique(Nordic$LBTESTCD) # 6 unique parameters from Nordic data
# #[1] C3M   C4M   PROC3 PROC4 PROC5 PROC6
# 
# unique(Siemens$LBTESTCD) # Siemen data holds the ELF_TEST reslt

# unique(GenfitDat$LBTESTCD) 
# "A2M"   "HBA1C" "NIS4"  "NISX" 

### check the correct subject ID to use in order to merge data
Nordic$SUBJID<-do.call("rbind",strsplit(as.character(Nordic$BARCODE), "LS"))[,1]
Nordic$SUBJID<-do.call("rbind",strsplit(Nordic$SUBJID, "N"))[,2]

PROC3$SUBJID<-do.call("rbind",strsplit(as.character(PROC3$BARCODE), "LS"))[,1]
PROC3$SUBJID<-do.call("rbind",strsplit(PROC3$SUBJID, "N"))[,2]


Labcorp$SUBJID<-do.call("rbind",strsplit(as.character(Labcorp$`PATIENT NAME`), "L"))[,1]
Labcorp$SUBJID<-do.call("rbind",strsplit(Labcorp$SUBJID, "N"))[,2]

Siemens$SUBJID<-do.call("rbind",strsplit(as.character(Siemens$BARCODE), "LS"))[,1]
Siemens$SUBJID<-do.call("rbind",strsplit(Siemens$SUBJID, "N"))[,2]

#CRNDat$SUBJID<-do.call("rbind",strsplit(as.character(CRNDat$current_label), "LS"))[,1]
CRNDat$SUBJID<-do.call("rbind",strsplit(CRNDat$subjid, "N"))[,2]

GenfitDat$SUBJID<-do.call("rbind",strsplit(as.character(GenfitDat$BARCODE), "LS"))[,1]
GenfitDat$SUBJID<-do.call("rbind",strsplit(GenfitDat$SUBJID, "N"))[,2]



OWLDat$SUBJID<-do.call("rbind",strsplit(as.character(OWLDat$SAMPLE.ID), "LS"))[,1]
OWLDat$SUBJID<-do.call("rbind",strsplit(OWLDat$SUBJID, "N"))[,2]

FibrometerDat1$SUBJID<-do.call("rbind",strsplit(FibrometerDat1$SUBJID, "N"))[,2]
FibrometerDat2$SUBJID<-do.call("rbind",strsplit(FibrometerDat2$SUBJID, "N"))[,2]

MetaDat$SUBJID<-MetaDat$nash

# #check how many unique subjects in each data
# length(unique(Siemens$SUBJID))
# length(unique(Labcorp$SUBJID))
# length(unique(Nordic$SUBJID))
# length(unique(MetaDat$SUBJID))
# 
# sum(unique(Nordic$SUBJID) %in% unique(Siemens$SUBJID))
# sum(unique(Nordic$SUBJID) %in% unique(Labcorp$SUBJID))
# sum(unique(Labcorp$SUBJID) %in% unique(Siemens$SUBJID))
# sum(unique(MetaDat$SUBJID) %in% unique(Siemens$SUBJID))


#get the endpoints ready and handling the data
MetaDat$Fibrosis <-if_else(MetaDat$fibrosisn>=2,1,0)
MetaDat$Advanced_Fibrosis <-if_else(MetaDat$fibrosisn>=3,1,0)
MetaDat$Cirrhosis<-if_else(MetaDat$fibrosisn>=4,1,0)
MetaDat$Fibrosis_Excluding_Cirrhosis<-if_else(MetaDat$fibrosisn>=2,1,0); 
MetaDat$Fibrosis_Excluding_Cirrhosis[MetaDat$Cirrhosis==1]<-NA # this will be used to exclude subjects who are cirrhosis
MetaDat$NASH<-if_else(MetaDat$anynash==1,1,0)
MetaDat$NAS<-if_else(MetaDat$nas>=4,1,0)
MetaDat$At_Risk_NASH<-if_else( (MetaDat$NASH==1 & MetaDat$NAS==1 & MetaDat$Fibrosis==1),1,0)



Siemens$ELF<-Siemens$LBORRES

# update PROC3 becusae new data was provided on Nov 4 2021
# PROC3<-Nordic[Nordic$LBTEST=="Pro-C3",]
# PROC3$'Pro-C3'<-PROC3$LBORRES
# PROC3<-PROC3[,c("SUBJID","Pro-C3")]

PROC3$'Pro-C3'<-PROC3$LBORRES
PROC3<-PROC3[,c("SUBJID","Pro-C3")]


PROC3_ELISA<-Nordic[Nordic$LBTEST=="Pro-C3",]
PROC3_ELISA$'Pro-C3-ELISA'<-PROC3_ELISA$LBORRES
PROC3_ELISA<-PROC3_ELISA[,c("SUBJID","Pro-C3-ELISA")]


PROC4<-Nordic[Nordic$LBTEST=="Pro-C4",]
PROC4$'Pro-C4'<-PROC4$LBORRES
PROC4<-PROC4[,c("SUBJID","Pro-C4")]


PROC5<-Nordic[Nordic$LBTEST=="Pro-C5",]
PROC5$'Pro-C5'<-PROC5$LBORRES
PROC5<-PROC5[,c("SUBJID","Pro-C5")]


PROC6<-Nordic[Nordic$LBTEST=="Pro-C6",]
PROC6$'Pro-C6'<-PROC6$LBORRES
PROC6<-PROC6[,c("SUBJID","Pro-C6")]

ALT<-Labcorp[Labcorp$TEST_ORD_NAME=="ALT (SGPT)",]
ALT$ALT<-ALT$Result
ALT<-merge(ALT, CRNDat[,c("SUBJID","alt")],all=TRUE)
ALT$ALT[is.na(ALT$ALT)]<-ALT$alt[is.na(ALT$ALT)]
ALT<-ALT[,c("SUBJID","ALT")]

AST<-Labcorp[Labcorp$TEST_ORD_NAME=="AST (SGOT)",]
AST$AST<-AST$Result
AST<-merge(AST, CRNDat[,c("SUBJID","ast")],all=TRUE)
AST$AST[is.na(AST$AST)]<-AST$ast[is.na(AST$AST)]
AST<-AST[,c("SUBJID","AST")]

NIS4<-GenfitDat[GenfitDat$LBTESTCD=="NIS4",]
NIS4$NIS4<-NIS4$LBORRES
NIS4<-NIS4[,c("SUBJID","NIS4")]

OWLDat$OWL<-OWLDat$DIGANOSIS
OWL<-OWLDat[,c("SUBJID","OWL")]

#Agile4	Agile3Plus	FAST	FMVCTE	FMVCTE_light and FM3G V - FibrosisScore	CirrhosisScore	NAFLD - FibrosisScore
Agile4<-FibrometerDat1[,c("SUBJID","Agile4")]
Agile3Plus<-FibrometerDat1[,c("SUBJID","Agile3Plus")]
FAST<-FibrometerDat1[,c("SUBJID","FAST")]
FMVCTE<-FibrometerDat1[,c("SUBJID","FMVCTE")]
FMVCTE_light<-FibrometerDat1[,c("SUBJID","FMVCTE_light")]

NAFLD<-FibrometerDat2[,c("SUBJID","NAFLD...FibrosisScore")]; colnames(NAFLD)<-c("SUBJID","NAFLD")
CirrhosisScore<-FibrometerDat2[,c("SUBJID","CirrhosisScore")]
FM3GV<-FibrometerDat2[,c("SUBJID","FM3G.V...FibrosisScore")]; colnames(FM3GV)<-c("SUBJID","FM3GV")

#####################################################################################
################### creating the dataset ready for analysis #####################
#####################################################################################
Dat_ELF<-merge(Siemens[,c("SUBJID","LBTESTCD","ELF")], MetaDat[,List],by="SUBJID")
saveRDS(Dat_ELF,file="Dat_ELF.rds")

Dat_PROC3<-merge(PROC3, MetaDat[,List],by="SUBJID")
saveRDS(Dat_PROC3,file="Dat_PROC3.rds")


Dat_NIS4<-merge(NIS4, MetaDat[,List],by="SUBJID")
saveRDS(Dat_NIS4,file="Dat_NIS4.rds")



Dat_All<-merge(Siemens[,c("SUBJID","ELF")], MetaDat[,List],by="SUBJID")
Dat_All<-merge(PROC3,Dat_All,by="SUBJID")
Dat_All<-merge(PROC3_ELISA,Dat_All,by="SUBJID")
Dat_All<-merge(PROC4,Dat_All,by="SUBJID")
Dat_All<-merge(PROC5,Dat_All,by="SUBJID")
Dat_All<-merge(PROC6,Dat_All,by="SUBJID")
Dat_All<-merge(AST,Dat_All,by="SUBJID")
Dat_All<-merge(ALT,Dat_All,by="SUBJID")
Dat_All<-merge(NIS4,Dat_All,by="SUBJID")
Dat_All<-merge(OWL,Dat_All,by="SUBJID")
Dat_All<-merge(Agile4,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(Agile3Plus,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(FAST,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(FMVCTE,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(FMVCTE_light,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(NAFLD,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(CirrhosisScore,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(FM3GV,Dat_All,by="SUBJID",all.y = TRUE)

Dat_All$AGE<-floor(Dat_All$ageyrs)
# calculating FIB-4
#FIB4<-Age (years)×AST (U/L)/[PLT(109/L)×ALT1/2 (U/L)].  
Dat_All$'FIB-4'<-(Dat_All$AGE*Dat_All$AST)/(Dat_All$platelet *sqrt(Dat_All$ALT))

# calculating ADPAT
#ADPAT<-exp(log10(Age*Proc-C3/sqrt(PLT)) + Diabetes.  
Dat_All$ADAPT<-exp(log((Dat_All$AGE*Dat_All$'Pro-C3-ELISA')/sqrt(Dat_All$platelet),10))+ Dat_All$dm2  

saveRDS(Dat_All,file="Dat_All 220111.rds")


```
<br>
<br>

```{r For self-defined functions}


CutpointAnalysis<-function(Dat, Marker, Endpoint, Def_Endpoint){
  
  #only keep complete records
  Data<-Dat[complete.cases(Dat[,c(Marker,Endpoint)]),]
  
  #find optimum cutpoint
  opt_cut <- cutpointr(x=Data[,Marker],
                    class=Data[,Endpoint],
                    method =maximize_metric, 
                    metric = youden)
  
  # caculating P value
  AUC<-opt_cut["AUC"]$AUC
  a<- qnorm(AUC, mean=0, sd=1)*1.414
  n2=sum(Data[,Endpoint]==1)
  n1=sum(Data[,Endpoint]==0)
  Var_AUC<-( 0.0099*exp((-0.5)*a^2) )*( (5*a^2+8)/n2 + (a^2+8)/n1 ) 
  SE_AUC<-sqrt(Var_AUC)
  z.test<-(AUC-0.5)/SE_AUC
  Pvalue<- (1-pnorm(abs(z.test),mean=0,sd=1)) #this is 1-side test
  
  #create the AUC object
  if(substr(opt_cut["direction"]$direction,1,1) == ">"){
   ROC<-roc( Data[,Endpoint], Data[,Marker], direction="<")
  }else{
   ROC<-roc( Data[,Endpoint], Data[,Marker], direction=">")
  }
  
  
 
  FIT=list()
  FIT[["Biomarker"]]<-Data[,Marker];
  FIT[["Endpoint"]]<-Data[,Endpoint];
  FIT[["AUCROC"]]<-opt_cut["AUC"]$AUC
  FIT[["Youden_Index"]]<-opt_cut["youden"]$youden
  FIT[["PredictionStat"]]<-summary(opt_cut)$confusion_matrix[[1]][1,c("tp", "fp","tn","fn")]
  FIT[["Optimal_cutpoint"]]<-round(opt_cut["optimal_cutpoint"]$optimal_cutpoint,1)
  FIT[["Optimal_cutpoint_direction"]]<-opt_cut["direction"]$direction
  FIT[["Pvalue"]]<-Pvalue
  FIT[["SE_AUCROC"]]<-SE_AUC
  FIT[["Biomarker_name"]]<-Marker
  FIT[["Endpoint_name"]]<-Endpoint
  FIT[["Endpoint_pos_var"]]<-Def_Endpoint$Positive[Def_Endpoint$Endpoint.variables==Endpoint]
  FIT[["Endpoint_neg_var"]]<-Def_Endpoint$Negative[Def_Endpoint$Endpoint.variables==Endpoint]
  FIT[["ROC"]]<-ROC
  
  return(FIT)
 


```
<br>
<br>

\newpage
# Chapter II: Diagnostic Performance Tables by Biomarkers
<br>
<br>



## Table 14.2.2.1 Diagnostic performance of candidate biomarker ELF  
<br>
 

```{r ELF,echo=FALSE,results='asis',eval=FALSE}


Dat=Dat_All;
Marker="ELF" 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis","Fibrosis_Excluding_Cirrhosis")



for(i in 1:length(List_Endpoint_update)){
  
  Endpoint<-List_Endpoint_update[i]
  
  Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
  
  cat("Table 14.2.2.1 Diagnostic performance of ELF")
  
  Table<-Table_Fun(FIT=Output)
  print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("  ","  ","  ",sep="\n"))
  
  Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
  Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
    
  cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
  cat(paste("  ","  ","  ",sep="\n"))
  cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
  cat(paste("  ","  ","  ",sep="\n"))
  
  #AUC plot
  cat(paste0("Figure 14.2.2.1-A AUC plot of ELF on endpoint ", Endpoint)) 
  plot(Output[["ROC"]]$sensitivities, Output[["ROC"]]$specificities, type="l", 
       xlab="Sensitivities", ylab="specificities",
       main=paste0("AUC plot of ELF on endpoint ", Endpoint),
       ylim=c(0,1),xlim=c(1,0), col="blue",lwd=2)
  abline(1,-1,lwd=2, lty=2)

  #PPV and NPV vs the prevalence on X-Axis
  cat(paste0("Figure 14.2.2.1-B PPV and NPV plot of ELF on endpoint ", Endpoint))
  TP<-Output$PredictionStat$tp; TN<-Output$PredictionStat$tn; FP<-Output$PredictionStat$fp; FN<-Output$PredictionStat$fn
  Sensitivity<-TP/sum(TP+FN) 
  Specificity<-TN/sum(FP+TN) 
  Prevalence<-seq(0,1,by=0.01)
  PPV<- (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) )
  NPV<- (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) )
  # PPV and NPV data for plot
  PPV_NPV_Dat<-data.frame(Prevalence=c(Prevalence,Prevalence),
                         Type=rep(c("PPV","NPV"), each =length(Prevalence)),
                         Val= c(PPV, NPV))
  PPVNPVplot<-ggplot(PPV_NPV_Dat, aes(x=Prevalence*100, y= Val, color=Type)) +
              geom_line(lwd=1.5) +  
              theme_bw()   +
              xlab("Prevalence Rate (%)") +
              ylab("Predictive Value (%)") +
              scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
              scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
              theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                    plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                    plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                    axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
 print(PPVNPVplot)
 
 # for table Predictive values of biomarker panels for their intended use in populations with varying prevalence of disease phenotype
 Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
 PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
 NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
 Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
                         PPV=PPV,
                         NPV=NPV,
                         Val=paste0(PPV,"%/",NPV,"%"))
 
 rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
 write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker, " on endpoint ", Endpoint,".csv"))

}

```
<br>


## Table 14.2.2.2 Diagnostic performance of candidate Fibrometer biomarkers
<br>
 

```{r FibrosisScore,echo=FALSE,results='asis',eval=FALSE}


Dat=Dat_All;
#Marker_list<-c("FM3GV", "CirrhosisScore", "NAFLD")
Marker_list<-c("FMVCTE")
 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis","Fibrosis_Excluding_Cirrhosis")

for(i in 1:length(Marker_list)){
  
    Marker<-Marker_list[i]
    
    for(j in 1:length(List_Endpoint_update)){
      
    Endpoint<-List_Endpoint_update[j]
    
    Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    
    cat(paste0("Table 14.2.2.2.",i, " Diagnostic performance of ", Marker))
    
    Table<-Table_Fun(FIT=Output)
    print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
    
    Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
    Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
      
    cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
    cat(paste("  ","  ","  ",sep="\n"))
    
    #AUC plot
    cat(paste0("Figure 14.2.2.2-A AUC plot of ", Marker, " on endpoint ", Endpoint)) 
    plot(Output[["ROC"]]$sensitivities, Output[["ROC"]]$specificities, type="l", 
         xlab="Sensitivities", ylab="specificities",
         main=paste0("AUC plot of ", Marker, " on endpoint ", Endpoint),
         ylim=c(0,1),xlim=c(1,0), col="blue",lwd=2)
    abline(1,-1,lwd=2, lty=2)
    
     #PPV and NPV vs the prevalence on X-Axis
    cat(paste0("Figure 14.2.2.2-B PPV and NPV plot of ", Marker, " on endpoint ", Endpoint)) 
    TP<-Output$PredictionStat$tp; TN<-Output$PredictionStat$tn; FP<-Output$PredictionStat$fp; FN<-Output$PredictionStat$fn
    Sensitivity<-TP/sum(TP+FN) 
    Specificity<-TN/sum(FP+TN) 
    Prevalence<-seq(0,1,by=0.01)
    PPV<- (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) )
    NPV<- (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) )
    # PPV and NPV data for plot
    PPV_NPV_Dat<-data.frame(Prevalence=c(Prevalence,Prevalence),
                           Type=rep(c("PPV","NPV"), each =length(Prevalence)),
                           Val= c(PPV, NPV))
    PPVNPVPlot<-ggplot(PPV_NPV_Dat, aes(x=Prevalence*100, y= Val, color=Type)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Prevalence Rate (%)") +
                        ylab("Predictive Value (%)") +
                        scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")

   print(PPVNPVPlot)
   
   
    
   # for table Predictive values of biomarker panels for their intended use in populations with varying prevalence of disease phenotype
   Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
                           PPV=PPV,
                           NPV=NPV,
                           Val=paste0(PPV,"%/",NPV,"%"))
   
   rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker, " on endpoint ", Endpoint,".csv"))

    
    }
  }



```
<br>

## Table 14.2.2.3 Diagnostic performance of candidate biomarker NIS4  
<br>
 

```{r NIS4,echo=FALSE,results='asis',eval=FALSE}


Dat=Dat_All;
Marker="NIS4" 
List_Endpoint_update<-c("NASH","NAS","At_Risk_NASH","Fibrosis","Advanced_Fibrosis","Cirrhosis","Fibrosis_Excluding_Cirrhosis")



for(i in 1:length(List_Endpoint_update)){
  
  Endpoint<-List_Endpoint_update[i]
  
  Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
  
  cat("Table 14.2.2.3 Diagnostic performance of NIS4")
  
  Table<-Table_Fun(FIT=Output)
  print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("  ","  ","  ",sep="\n"))
  
  Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
  Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
    
  cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
  cat(paste("  ","  ","  ",sep="\n"))
  cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
  cat(paste("  ","  ","  ",sep="\n"))

  #AUC plot
  cat(paste0("Figure 14.2.2.3-A AUC plot of NIS4 on endpoint ", Endpoint)) 
  plot(Output[["ROC"]]$sensitivities, Output[["ROC"]]$specificities, type="l", 
       xlab="Sensitivities", ylab="specificities",
       main=paste0("AUC plot of NIS4 on endpoint ", Endpoint),
       ylim=c(0,1),xlim=c(1,0), col="blue",lwd=2)
  abline(1,-1,lwd=2, lty=2)
  
  #PPV and NPV vs the prevalence on X-Axis
  cat(paste0("Figure 14.2.2.3-B PPV and NPV plot of NIS4 on endpoint ", Endpoint)) 
  TP<-Output$PredictionStat$tp; TN<-Output$PredictionStat$tn; FP<-Output$PredictionStat$fp; FN<-Output$PredictionStat$fn
  Sensitivity<-TP/sum(TP+FN) 
  Specificity<-TN/sum(FP+TN) 
  Prevalence<-seq(0,1,by=0.01)
  PPV<- (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) )
  NPV<- (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) )
  # PPV and NPV data for plot
  PPV_NPV_Dat<-data.frame(Prevalence=c(Prevalence,Prevalence),
                         Type=rep(c("PPV","NPV"), each =length(Prevalence)),
                         Val= c(PPV, NPV))
  PPVNPVPlot<-ggplot(PPV_NPV_Dat, aes(x=Prevalence*100, y= Val, color=Type)) +
                      geom_line(lwd=1.5) +  
                      theme_bw()   +
                      xlab("Prevalence Rate (%)") +
                      ylab("Predictive Value (%)") +
                      scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                      scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                          theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                    plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                    plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                    axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")

 print(PPVNPVPlot)
 
    # for table Predictive values of biomarker panels for their intended use in populations with varying prevalence of disease phenotype
   Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
                           PPV=PPV,
                           NPV=NPV,
                           Val=paste0(PPV,"%/",NPV,"%"))
   
   rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker, " on endpoint ", Endpoint,".csv"))
  


}



```
<br>


## Table 14.2.2.4 Diagnostic performance of candidate biomarker OWL  
<br>
 

```{r OWL,echo=FALSE,results='asis',eval=FALSE}


Dat=Dat_All;
Marker="OWL" 
List_Endpoint_update<-c("NASH","NAS")

for(i in 1:length(List_Endpoint_update)){
  
  Endpoint<-List_Endpoint_update[i]
  
  Output<-CutpointAnalysis_Catalog(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
  
  cat("Table 14.2.2.4 Diagnostic performance of OWL")
  
  Table<-Table_Fun_Catalog(FIT=Output)
  print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("  ","  ","  ",sep="\n"))
  
  Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
  Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
    
  cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
  cat(paste("  ","  ","  ",sep="\n"))
  cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
  cat(paste("  ","  ","  ",sep="\n"))
  
  #AUC plot
  cat(paste0("Figure 14.2.2.4 AUC plot of OWL on endpoint ", Endpoint)) 
  plot(Output[["ROC"]]$sensitivities, Output[["ROC"]]$specificities, type="l", 
       xlab="Sensitivities", ylab="specificities",
       main=paste0("AUC plot of OWL on endpoint ", Endpoint),
       ylim=c(0,1),xlim=c(1,0), col="blue",lwd=2)
  abline(1,-1,lwd=2, lty=2)



}



```
<br>


## Table 14.2.2.5 Diagnostic performance of candidate biomarker Pro-C3 (COMBAS)   
<br>
 

```{r PROC3,echo=FALSE,results='asis',eval=FALSE}


Dat=Dat_All;
Marker="Pro-C3" 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")

for(i in 1:length(List_Endpoint_update)){
  
  Endpoint<-List_Endpoint_update[i]
  
  Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
  
  cat("Table 14.2.2.5 Diagnostic performance of Pro-C3")
  
  Table<-Table_Fun(FIT=Output)
  print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("  ","  ","  ",sep="\n"))
  
  Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
  Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
    
  cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
  cat(paste("  ","  ","  ",sep="\n"))
  cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
  cat(paste("  ","  ","  ",sep="\n"))
  
  #AUC plot
  cat(paste0("Figure 14.2.2.5-A AUC plot of Pro-C3 on endpoint ", Endpoint)) 
  plot(Output[["ROC"]]$sensitivities, Output[["ROC"]]$specificities, type="l", 
       xlab="Sensitivities", ylab="specificities",
       main=paste0("AUC plot of Pro-C3 on endpoint ", Endpoint),
       ylim=c(0,1),xlim=c(1,0), col="blue",lwd=2)
  abline(1,-1,lwd=2, lty=2)
  
  #PPV and NPV vs the prevalence on X-Axis
  cat(paste0("Figure 14.2.2.5-B PPV and NPV plot of Pro-C3 on endpoint ", Endpoint))
  TP<-Output$PredictionStat$tp; TN<-Output$PredictionStat$tn; FP<-Output$PredictionStat$fp; FN<-Output$PredictionStat$fn
  Sensitivity<-TP/sum(TP+FN) 
  Specificity<-TN/sum(FP+TN) 
  Prevalence<-seq(0,1,by=0.01)
  PPV<- (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) )
  NPV<- (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) )
  # PPV and NPV data for plot
  PPV_NPV_Dat<-data.frame(Prevalence=c(Prevalence,Prevalence),
                         Type=rep(c("PPV","NPV"), each =length(Prevalence)),
                         Val= c(PPV, NPV))
  PPVNPVPlot<-ggplot(PPV_NPV_Dat, aes(x=Prevalence*100, y= Val, color=Type)) +
                      geom_line(lwd=1.5) +  
                      theme_bw()   +
                      xlab("Prevalence Rate (%)") +
                      ylab("Predictive Value (%)") +
                      scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                      scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                          theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                    plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                    plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                    axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")

 print(PPVNPVPlot)
 
    # for table Predictive values of biomarker panels for their intended use in populations with varying prevalence of disease phenotype
   Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
                           PPV=PPV,
                           NPV=NPV,
                           Val=paste0(PPV,"%/",NPV,"%"))
   
   rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker, " on endpoint ", Endpoint,".csv"))
  



}



```
<br>

## Table 14.2.2.6 Diagnostic performance of candidate biomarker Pro-C4  
<br>
 

```{r PROC4,echo=FALSE,results='asis',eval=FALSE}


Dat=Dat_All;
Marker="Pro-C4" 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")

for(i in 1:length(List_Endpoint_update)){
  
  Endpoint<-List_Endpoint_update[i]
  
  Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
  
  cat("Table 14.2.2.6 Diagnostic performance of Pro-C4")
  
  Table<-Table_Fun(FIT=Output)
  print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("  ","  ","  ",sep="\n"))
  
  Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
  Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
    
  cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
  cat(paste("  ","  ","  ",sep="\n"))
  cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
  cat(paste("  ","  ","  ",sep="\n"))
  
  #AUC plot
  cat(paste0("Figure 14.2.2.6 AUC plot of Pro-C4 on endpoint ", Endpoint)) 
  plot(Output[["ROC"]]$sensitivities, Output[["ROC"]]$specificities, type="l", 
       xlab="Sensitivities", ylab="specificities",
       main=paste0("AUC plot of Pro-C4 on endpoint ", Endpoint),
       ylim=c(0,1),xlim=c(1,0), col="blue",lwd=2)
  abline(1,-1,lwd=2, lty=2)


  

}



```
<br>


## Table 14.2.2.7 Diagnostic performance of candidate biomarker Pro-C5  
<br>
 

```{r PROC5,echo=FALSE,results='asis',eval=FALSE}


Dat=Dat_All;
Marker="Pro-C5" 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")

for(i in 1:length(List_Endpoint_update)){
  
  Endpoint<-List_Endpoint_update[i]
  
  Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
  
  cat("Table 14.2.2.7 Diagnostic performance of Pro-C5")
  
  Table<-Table_Fun(FIT=Output)
  print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("  ","  ","  ",sep="\n"))
  
  Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
  Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
    
  cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
  cat(paste("  ","  ","  ",sep="\n"))
  cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
  cat(paste("  ","  ","  ",sep="\n"))
  
    #AUC plot
  cat(paste0("Figure 14.2.2.7 AUC plot of Pro-C5 on endpoint ", Endpoint)) 
  plot(Output[["ROC"]]$sensitivities, Output[["ROC"]]$specificities, type="l", 
       xlab="Sensitivities", ylab="specificities",
       main=paste0("AUC plot of Pro-C5 on endpoint ", Endpoint),
       ylim=c(0,1),xlim=c(1,0), col="blue",lwd=2)
  abline(1,-1,lwd=2, lty=2)



}



```
<br>



## Table 14.2.2.8 Diagnostic performance of candidate biomarker Pro-C6  
<br>
 

```{r PROC6,echo=FALSE,results='asis',eval=FALSE}


Dat=Dat_All;
Marker="Pro-C6" 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")

for(i in 1:length(List_Endpoint_update)){
  
  Endpoint<-List_Endpoint_update[i]
  
  Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
  
  cat("Table 14.2.2.8 Diagnostic performance of Pro-C6")
  
  Table<-Table_Fun(FIT=Output)
  print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("  ","  ","  ",sep="\n"))
  
  Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
  Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
    
  cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
  cat(paste("  ","  ","  ",sep="\n"))
  cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
  cat(paste("  ","  ","  ",sep="\n"))
  
  #AUC plot
  cat(paste0("Figure 14.2.2.8 AUC plot of Pro-C6 on endpoint ", Endpoint)) 
  plot(Output[["ROC"]]$sensitivities, Output[["ROC"]]$specificities, type="l", 
       xlab="Sensitivities", ylab="specificities",
       main=paste0("AUC plot of Pro-C6 on endpoint ", Endpoint),
       ylim=c(0,1),xlim=c(1,0), col="blue",lwd=2)
  abline(1,-1,lwd=2, lty=2)



}



```
<br>




## Table 14.2.2.9 Diagnostic performance of candidate biomarker ADAPT 
<br>
 

```{r ADAPT,echo=FALSE,results='asis',eval=FALSE}


Dat=Dat_All;
Marker="ADAPT" 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")

for(i in 1:length(List_Endpoint_update)){
  
  Endpoint<-List_Endpoint_update[i]
  
  Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
  
  cat("Table 14.2.2.9 Diagnostic performance of ADAPT")
  
  Table<-Table_Fun(FIT=Output)
  print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("  ","  ","  ",sep="\n"))
  
  Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
  Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
    
  cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
  cat(paste("  ","  ","  ",sep="\n"))
  cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
  cat(paste("  ","  ","  ",sep="\n"))
  
  #AUC plot
  cat(paste0("Figure 14.2.2.9 AUC plot of ADAPT on endpoint ", Endpoint)) 
  plot(Output[["ROC"]]$sensitivities, Output[["ROC"]]$specificities, type="l", 
       xlab="Sensitivities", ylab="specificities",
       main=paste0("AUC plot of ADAPT on endpoint ", Endpoint),
       ylim=c(0,1),xlim=c(1,0), col="blue",lwd=2,
       cex.lab=1.8, cex.axis=1.5, cex.main=1.5, cex.sub=1.5)
  abline(1,-1,lwd=2, lty=2)
  
  cat(paste("  ","  ","  ",sep="\n"))
  cat(paste("  ","  ","  ",sep="\n"))


}



```
<br>

# Chapter IV: Comparison of the diagnostic performance of candidate marker versus biomarker 

## Table 14.2.4.1 Comparison of the diagnostic performance of ELF versus FIB-4   
<br>
 

```{r ELFvsFIB-4,echo=FALSE,results='asis',eval=TRUE}

Marker1="ELF" # bio-marker 
Marker2="FIB-4" #candidate marker

List_Endpoint_update<-c("At_Risk_NASH","Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
    Endpoint<-List_Endpoint_update[i]
    Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 
    
    Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    
    cat("Table 14.2.4.1 Comparison of the diagnostic performance of ELF versus FIB-4")
    
    Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)
    
    print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
    
    Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
    Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
      
    cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
    cat(paste("  ","  ","  ",sep="\n"))
  
    
    #AUC plot
    cat(paste0("Figure 14.2.4.1.",i,"-A AUC plot of ", Marker1, " and ", Marker2, " on the endpoint ", Endpoint)) 
    ROC_Dat<-data.frame(Marker=c(rep(Marker1, length(Output_Biomarker[["ROC"]]$sensitivities)), 
                                 rep(Marker2, length(Output_Candidate[["ROC"]]$sensitivities))),
                        Sensitivity=c(Output_Biomarker[["ROC"]]$sensitivities,Output_Candidate[["ROC"]]$sensitivities),
                        Specificity= c(Output_Biomarker[["ROC"]]$specificities,Output_Candidate[["ROC"]]$specificities))  
    ROCPlot<-ggplot(ROC_Dat, aes(x=Sensitivity*100, y= Specificity*100, color=Marker)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Sensitivities(%)") +
                        ylab("Specificities(%)")+
                        scale_x_reverse(breaks=seq(from=0, to=100, by=5))+
                        #scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
  
    print(ROCPlot)
  
      
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
    
    
    #PPV and NPV vs the prevalence on X-Axis
    cat(paste0("Figure 14.2.4.1.",i,"-B PPV and NPV plot of ", Marker1, " on the endpoint ", Endpoint))
    TP<-Output_Biomarker$PredictionStat$tp; TN<-Output_Biomarker$PredictionStat$tn; FP<-Output_Biomarker$PredictionStat$fp; FN<-Output_Biomarker$PredictionStat$fn
    Sensitivity<-TP/sum(TP+FN) 
    Specificity<-TN/sum(FP+TN) 
    Prevalence<-seq(0,1,by=0.01)
    PPV<- (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) )
    NPV<- (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) )
    # PPV and NPV data for plot
    PPV_NPV_Dat<-data.frame(Prevalence=c(Prevalence,Prevalence),
                           Type=rep(c("PPV","NPV"), each =length(Prevalence)),
                           Val= c(PPV, NPV))
    PPVNPVPlot<-ggplot(PPV_NPV_Dat, aes(x=Prevalence*100, y= Val, color=Type)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Prevalence Rate (%)") +
                        ylab("Predictive Value (%)") +
                        scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
  
   print(PPVNPVPlot)
   
   
  ###for table Predictive values of bio-marker panels for their intended use in populations with varying prevalence of disease phenotype for Marker 1
  TP<-Output_Biomarker$PredictionStat$tp; TN<-Output_Biomarker$PredictionStat$tn; FP<-Output_Biomarker$PredictionStat$fp; FN<-Output_Biomarker$PredictionStat$fn
  Sensitivity<-TP/sum(TP+FN) 
  Specificity<-TN/sum(FP+TN) 
   Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
                           PPV=PPV,
                           NPV=NPV,
                           Val=paste0(PPV,"%/",NPV,"%"))
   
   rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker1," on endpoint ", Endpoint,".csv"))
   
   
      
  ###for table Predictive values of bio-marker panels for their intended use in populations with varying prevalence of disease phenotype for Marker 2
    TP<-Output_Candidate$PredictionStat$tp; TN<-Output_Candidate$PredictionStat$tn; FP<-Output_Candidate$PredictionStat$fp; FN<-Output_Candidate$PredictionStat$fn
    Sensitivity<-TP/sum(TP+FN) 
    Specificity<-TN/sum(FP+TN) 
   Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
                           PPV=PPV,
                           NPV=NPV,
                           Val=paste0(PPV,"%/",NPV,"%"))
   
   rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker2," on endpoint ", Endpoint,".csv"))


}



```
<br>



## Table 14.2.4.2 Comparison of the diagnostic performance of Fibrometer biomarkers versus FIB-4   
<br>
 

```{r FibrometervsFIB-4,echo=FALSE,results='asis',eval=TRUE}

#Marker_list<-c("FM3GV", "CirrhosisScore", "NAFLD", "FMVCTE_light", "FMVCTE", "FAST", "Agile3Plus", "Agile4")
Marker_list<-c("FMVCTE")
Marker2="FIB-4" #candidate marker

List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")

 for(i in 1:length(Marker_list)){
   
    Marker1<-Marker_list[i]
     
    for(j in 1:length(List_Endpoint_update)){
      
    Endpoint<-List_Endpoint_update[j]
    Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 
    
    Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    
    cat(paste0("Table 14.2.4.2.",i," Comparison of the diagnostic performance of ", Marker1," versus FIB-4"))
    
    Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)
    
    print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
    
    Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
    Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
      
    cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
    cat(paste("  ","  ","  ",sep="\n"))
    
     #AUC plot
    cat(paste0("Figure 14.2.4.2.",i,"-A AUC plot of ", Marker1, " and ", Marker2, " on the endpoint ",Endpoint)) 
    ROC_Dat<-data.frame(Marker=c(rep(Marker1, length(Output_Biomarker[["ROC"]]$sensitivities)), 
                                 rep(Marker2, length(Output_Candidate[["ROC"]]$sensitivities))),
                        Sensitivity=c(Output_Biomarker[["ROC"]]$sensitivities,Output_Candidate[["ROC"]]$sensitivities),
                        Specificity= c(Output_Biomarker[["ROC"]]$specificities,Output_Candidate[["ROC"]]$specificities))  
    ROCPlot<-ggplot(ROC_Dat, aes(x=Sensitivity*100, y= Specificity*100, color=Marker)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Sensitivities(%)") +
                        ylab("Specificities(%)")+
                        scale_x_reverse(breaks=seq(from=0, to=100, by=5))+
                        #scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
  
    print(ROCPlot)
    
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
  
    #PPV and NPV vs the prevalence on X-Axis
    cat(paste0("Figure 14.2.4.2.",i,"-B PPV and NPV plot of ", Marker1, " on the endpoint ", Endpoint)) 
    TP<-Output_Biomarker$PredictionStat$tp; TN<-Output_Biomarker$PredictionStat$tn; FP<-Output_Biomarker$PredictionStat$fp; FN<-Output_Biomarker$PredictionStat$fn
    Sensitivity<-TP/sum(TP+FN) 
    Specificity<-TN/sum(FP+TN) 
    Prevalence<-seq(0,1,by=0.01)
    PPV<- (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) )
    NPV<- (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) )
    # PPV and NPV data for plot
    PPV_NPV_Dat<-data.frame(Prevalence=c(Prevalence,Prevalence),
                           Type=rep(c("PPV","NPV"), each =length(Prevalence)),
                           Val= c(PPV, NPV))
    PPVNPVPlot<-ggplot(PPV_NPV_Dat, aes(x=Prevalence*100, y= Val, color=Type)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Prevalence Rate (%)") +
                        ylab("Predictive Value (%)") +
                        scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
  
   print(PPVNPVPlot)
   
     ###for table Predictive values of bio-marker panels for their intended use in populations with varying prevalence of disease phenotype for Marker 1
  TP<-Output_Biomarker$PredictionStat$tp; TN<-Output_Biomarker$PredictionStat$tn; FP<-Output_Biomarker$PredictionStat$fp; FN<-Output_Biomarker$PredictionStat$fn
  Sensitivity<-TP/sum(TP+FN) 
  Specificity<-TN/sum(FP+TN) 
   Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
                           PPV=PPV,
                           NPV=NPV,
                           Val=paste0(PPV,"%/",NPV,"%"))
   
   rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker1," on endpoint ", Endpoint,".csv"))
   
   
      
  ###for table Predictive values of bio-marker panels for their intended use in populations with varying prevalence of disease phenotype for Marker 2
   #  TP<-Output_Candidate$PredictionStat$tp; TN<-Output_Candidate$PredictionStat$tn; FP<-Output_Candidate$PredictionStat$fp; FN<-Output_Candidate$PredictionStat$fn
   #  Sensitivity<-TP/sum(TP+FN) 
   #  Specificity<-TN/sum(FP+TN) 
   # Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   # PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   # NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   # Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
   #                         PPV=PPV,
   #                         NPV=NPV,
   #                         Val=paste0(PPV,"%/",NPV,"%"))
   # 
   # rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   # write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker2," on endpoint ", Endpoint,".csv"))

    
      
    }
 }


```
<br>


## Table 14.2.4.3 Comparison of the diagnostic performance of NIS4 versus ALT   
<br>
 

```{r NIS4vsALT,echo=FALSE,results='asis',eval=TRUE}

Marker1="NIS4" # bio-marker 
Marker2="ALT" #candidate marker

List_Endpoint_update<-c("NASH","NAS","At_Risk_NASH","Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
      
    Endpoint<-List_Endpoint_update[i]
    Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 
    
    Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    
    cat("Table 14.2.4.3 Comparison of the diagnostic performance of NIS4 versus ALT")
    
    Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)
    
    print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
    
    Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
    Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
      
    cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
    cat(paste("  ","  ","  ",sep="\n"))

    #AUC plot
    cat(paste0("Figure 14.2.4.3.",i,"-A AUC plot of ", Marker1, " and ", Marker2, " on the endpoint ",Endpoint)) 
    ROC_Dat<-data.frame(Marker=c(rep(Marker1, length(Output_Biomarker[["ROC"]]$sensitivities)), 
                                 rep(Marker2, length(Output_Candidate[["ROC"]]$sensitivities))),
                        Sensitivity=c(Output_Biomarker[["ROC"]]$sensitivities,Output_Candidate[["ROC"]]$sensitivities),
                        Specificity= c(Output_Biomarker[["ROC"]]$specificities,Output_Candidate[["ROC"]]$specificities))  
    ROCPlot<-ggplot(ROC_Dat, aes(x=Sensitivity*100, y= Specificity*100, color=Marker)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Sensitivities(%)") +
                        ylab("Specificities(%)")+
                        scale_x_reverse(breaks=seq(from=0, to=100, by=5))+
                        #scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
  
    print(ROCPlot)
      
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
  
    #PPV and NPV vs the prevalence on X-Axis
    cat(paste0("Figure 14.2.4.3.",i,"-B PPV and NPV plot of ", Marker1, " on the endpoint ", Endpoint)) 
    TP<-Output_Biomarker$PredictionStat$tp; TN<-Output_Biomarker$PredictionStat$tn; FP<-Output_Biomarker$PredictionStat$fp; FN<-Output_Biomarker$PredictionStat$fn
    Sensitivity<-TP/sum(TP+FN) 
    Specificity<-TN/sum(FP+TN) 
    Prevalence<-seq(0,1,by=0.01)
    PPV<- (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) )
    NPV<- (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) )
    # PPV and NPV data for plot
    PPV_NPV_Dat<-data.frame(Prevalence=c(Prevalence,Prevalence),
                           Type=rep(c("PPV","NPV"), each =length(Prevalence)),
                           Val= c(PPV, NPV))
    PPVNPVPlot<-ggplot(PPV_NPV_Dat, aes(x=Prevalence*100, y= Val, color=Type)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Prevalence Rate (%)") +
                        ylab("Predictive Value (%)") +
                        scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
  
   print(PPVNPVPlot)
   
     ###for table Predictive values of bio-marker panels for their intended use in populations with varying prevalence of disease phenotype for Marker 1
  TP<-Output_Biomarker$PredictionStat$tp; TN<-Output_Biomarker$PredictionStat$tn; FP<-Output_Biomarker$PredictionStat$fp; FN<-Output_Biomarker$PredictionStat$fn
  Sensitivity<-TP/sum(TP+FN) 
  Specificity<-TN/sum(FP+TN) 
   Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
                           PPV=PPV,
                           NPV=NPV,
                           Val=paste0(PPV,"%/",NPV,"%"))
   
   rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker1," on endpoint ", Endpoint,".csv"))
   
   
      
  ###for table Predictive values of bio-marker panels for their intended use in populations with varying prevalence of disease phenotype for Marker 2
    TP<-Output_Candidate$PredictionStat$tp; TN<-Output_Candidate$PredictionStat$tn; FP<-Output_Candidate$PredictionStat$fp; FN<-Output_Candidate$PredictionStat$fn
    Sensitivity<-TP/sum(TP+FN) 
    Specificity<-TN/sum(FP+TN) 
   Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
                           PPV=PPV,
                           NPV=NPV,
                           Val=paste0(PPV,"%/",NPV,"%"))
   
   rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker2," on endpoint ", Endpoint,".csv"))

    

}



```
<br>


## Table 14.2.4.4 Comparison of the diagnostic performance of NIS4 versus FIB-4   
<br>
 

```{r NIS4vsFIB-4,echo=FALSE,results='asis',eval=TRUE}

Marker1="NIS4" # bio-marker 
Marker2="FIB-4" #candidate marker

List_Endpoint_update<-c("NASH","NAS","At_Risk_NASH","Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
    Endpoint<-List_Endpoint_update[i]
    Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 
    
    Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    
    cat("Table 14.2.4.4 Comparison of the diagnostic performance of NIS4 versus FIB-4")
    
    Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)
    
    print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
    
    Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
    Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
      
    cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
    cat(paste("  ","  ","  ",sep="\n"))
    
    #AUC plot
    cat(paste0("Figure 14.2.4.4.",i,"-A AUC plot of ", Marker1, " and ", Marker2, " on the endpoint ",Endpoint)) 
    ROC_Dat<-data.frame(Marker=c(rep(Marker1, length(Output_Biomarker[["ROC"]]$sensitivities)), 
                                 rep(Marker2, length(Output_Candidate[["ROC"]]$sensitivities))),
                        Sensitivity=c(Output_Biomarker[["ROC"]]$sensitivities,Output_Candidate[["ROC"]]$sensitivities),
                        Specificity= c(Output_Biomarker[["ROC"]]$specificities,Output_Candidate[["ROC"]]$specificities))  
    ROCPlot<-ggplot(ROC_Dat, aes(x=Sensitivity*100, y= Specificity*100, color=Marker)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Sensitivities(%)") +
                        ylab("Specificities(%)")+
                        scale_x_reverse(breaks=seq(from=0, to=100, by=5))+
                        #scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
  
    print(ROCPlot)
    
        
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
  
  
    #PPV and NPV vs the prevalence on X-Axis
    cat(paste0("Figure 14.2.4.4.",i,"-B PPV and NPV plot of ", Marker1, " on the endpoint ", Endpoint)) 
    TP<-Output_Biomarker$PredictionStat$tp; TN<-Output_Biomarker$PredictionStat$tn; FP<-Output_Biomarker$PredictionStat$fp; FN<-Output_Biomarker$PredictionStat$fn
    Sensitivity<-TP/sum(TP+FN) 
    Specificity<-TN/sum(FP+TN) 
    Prevalence<-seq(0,1,by=0.01)
    PPV<- (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) )
    NPV<- (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) )
    # PPV and NPV data for plot
    PPV_NPV_Dat<-data.frame(Prevalence=c(Prevalence,Prevalence),
                           Type=rep(c("PPV","NPV"), each =length(Prevalence)),
                           Val= c(PPV, NPV))
    PPVNPVPlot<-ggplot(PPV_NPV_Dat, aes(x=Prevalence*100, y= Val, color=Type)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Prevalence Rate (%)") +
                        ylab("Predictive Value (%)") +
                        scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
  
   print(PPVNPVPlot)
   
     ###for table Predictive values of bio-marker panels for their intended use in populations with varying prevalence of disease phenotype for Marker 1
  TP<-Output_Biomarker$PredictionStat$tp; TN<-Output_Biomarker$PredictionStat$tn; FP<-Output_Biomarker$PredictionStat$fp; FN<-Output_Biomarker$PredictionStat$fn
  Sensitivity<-TP/sum(TP+FN) 
  Specificity<-TN/sum(FP+TN) 
   Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
                           PPV=PPV,
                           NPV=NPV,
                           Val=paste0(PPV,"%/",NPV,"%"))
   
   rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker1," on endpoint ", Endpoint,".csv"))
   
   
      
  ###for table Predictive values of bio-marker panels for their intended use in populations with varying prevalence of disease phenotype for Marker 2
   #  TP<-Output_Candidate$PredictionStat$tp; TN<-Output_Candidate$PredictionStat$tn; FP<-Output_Candidate$PredictionStat$fp; FN<-Output_Candidate$PredictionStat$fn
   #  Sensitivity<-TP/sum(TP+FN) 
   #  Specificity<-TN/sum(FP+TN) 
   # Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   # PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   # NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   # Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
   #                         PPV=PPV,
   #                         NPV=NPV,
   #                         Val=paste0(PPV,"%/",NPV,"%"))
   # 
   # rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   # write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker2," on endpoint ", Endpoint,".csv"))


}



```
<br>

## Table 14.2.4.5 Comparison of the diagnostic performance of OWL versus ALT   
<br>
 

```{r OWLvsALT,echo=FALSE,results='asis',eval=FALSE}

Marker1="OWL" # bio-marker 
Marker2="ALT" #candidate marker

List_Endpoint_update<-c("NASH","NAS")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 

Output_Biomarker<-CutpointAnalysis_Catalog(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.5 Comparison of the diagnostic performance of NIS4 versus ALT")

Table<-Table_Fun_Comparison_Catalog(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>



## Table 14.2.4.6.1 Comparison of the diagnostic performance of Pro-C3(COBAS) versus FIB-4     
<br>
 

```{r RPOC3-COBASvsFIB-4,echo=FALSE,results='asis',eval=TRUE}


Marker1="Pro-C3" # bio-marker 
Marker2="FIB-4" #candidate marker
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
    Endpoint<-List_Endpoint_update[i]
    Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 
    
    
    Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    
    cat("Table 14.2.4.6.1 Comparison of the diagnostic performance of Pro-C3 versus FIB-4")
    
    Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)
    
    print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
    
    Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
    Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
      
    cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
    cat(paste("  ","  ","  ",sep="\n"))
    
    #AUC plot
    cat(paste0("Figure 14.2.4.6.1","-A AUC plot of ", Marker1, " and ", Marker2, " on the endpoint ",Endpoint)) 
    ROC_Dat<-data.frame(Marker=c(rep(Marker1, length(Output_Biomarker[["ROC"]]$sensitivities)), 
                                 rep(Marker2, length(Output_Candidate[["ROC"]]$sensitivities))),
                        Sensitivity=c(Output_Biomarker[["ROC"]]$sensitivities,Output_Candidate[["ROC"]]$sensitivities),
                        Specificity= c(Output_Biomarker[["ROC"]]$specificities,Output_Candidate[["ROC"]]$specificities))  
    ROCPlot<-ggplot(ROC_Dat, aes(x=Sensitivity*100, y= Specificity*100, color=Marker)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Sensitivities(%)") +
                        ylab("Specificities(%)")+
                        scale_x_reverse(breaks=seq(from=0, to=100, by=5))+
                        #scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
  
    print(ROCPlot)
    
        
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
  
  
    #PPV and NPV vs the prevalence on X-Axis
    cat(paste0("Figure 14.2.4.6.1","-B PPV and NPV plot of ", Marker1, " on the endpoint ", Endpoint)) 
    TP<-Output_Biomarker$PredictionStat$tp; TN<-Output_Biomarker$PredictionStat$tn; FP<-Output_Biomarker$PredictionStat$fp; FN<-Output_Biomarker$PredictionStat$fn
    Sensitivity<-TP/sum(TP+FN) 
    Specificity<-TN/sum(FP+TN) 
    Prevalence<-seq(0,1,by=0.01)
    PPV<- (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) )
    NPV<- (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) )
    # PPV and NPV data for plot
    PPV_NPV_Dat<-data.frame(Prevalence=c(Prevalence,Prevalence),
                           Type=rep(c("PPV","NPV"), each =length(Prevalence)),
                           Val= c(PPV, NPV))
    PPVNPVPlot<-ggplot(PPV_NPV_Dat, aes(x=Prevalence*100, y= Val, color=Type)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Prevalence Rate (%)") +
                        ylab("Predictive Value (%)") +
                        scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
  
   print(PPVNPVPlot)
   
   
     ###for table Predictive values of bio-marker panels for their intended use in populations with varying prevalence of disease phenotype for Marker 1
  TP<-Output_Biomarker$PredictionStat$tp; TN<-Output_Biomarker$PredictionStat$tn; FP<-Output_Biomarker$PredictionStat$fp; FN<-Output_Biomarker$PredictionStat$fn
  Sensitivity<-TP/sum(TP+FN) 
  Specificity<-TN/sum(FP+TN) 
   Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
                           PPV=PPV,
                           NPV=NPV,
                           Val=paste0(PPV,"%/",NPV,"%"))
   
   rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker1," on endpoint ", Endpoint,".csv"))
   
   
      
  ###for table Predictive values of bio-marker panels for their intended use in populations with varying prevalence of disease phenotype for Marker 2
   #  TP<-Output_Candidate$PredictionStat$tp; TN<-Output_Candidate$PredictionStat$tn; FP<-Output_Candidate$PredictionStat$fp; FN<-Output_Candidate$PredictionStat$fn
   #  Sensitivity<-TP/sum(TP+FN) 
   #  Specificity<-TN/sum(FP+TN) 
   # Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   # PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   # NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   # Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
   #                         PPV=PPV,
   #                         NPV=NPV,
   #                         Val=paste0(PPV,"%/",NPV,"%"))
   # 
   # rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   # write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker2," on endpoint ", Endpoint,".csv"))


}



```
<br>




## Table 14.2.4.6.2 Comparison of the diagnostic performance of Pro-C3(ELISA) versus FIB-4  
<br>
 

```{r RPOC3-ELISAvsFIB-4,echo=FALSE,results='asis',eval=TRUE}


Marker1="Pro-C3-ELISA" # bio-marker 
Marker2="FIB-4" #candidate marker
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
    Endpoint<-List_Endpoint_update[i]
    Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 
    
    
    Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    
    cat("Table 14.2.4.6.2 Comparison of the diagnostic performance of Pro-C3 versus FIB-4")
    
    Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)
    
    print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
    
    Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
    Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
      
    cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
    cat(paste("  ","  ","  ",sep="\n"))
    
    #AUC plot
    cat(paste0("Figure 14.2.4.6.2","-A AUC plot of ", Marker1, " and ", Marker2, " on the endpoint ",Endpoint)) 
    ROC_Dat<-data.frame(Marker=c(rep(Marker1, length(Output_Biomarker[["ROC"]]$sensitivities)), 
                                 rep(Marker2, length(Output_Candidate[["ROC"]]$sensitivities))),
                        Sensitivity=c(Output_Biomarker[["ROC"]]$sensitivities,Output_Candidate[["ROC"]]$sensitivities),
                        Specificity= c(Output_Biomarker[["ROC"]]$specificities,Output_Candidate[["ROC"]]$specificities))  
    ROCPlot<-ggplot(ROC_Dat, aes(x=Sensitivity*100, y= Specificity*100, color=Marker)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Sensitivities(%)") +
                        ylab("Specificities(%)")+
                        scale_x_reverse(breaks=seq(from=0, to=100, by=5))+
                        #scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
  
    print(ROCPlot)
    
        
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
  
  
    #PPV and NPV vs the prevalence on X-Axis
    cat(paste0("Figure 14.2.4.6.2","-B PPV and NPV plot of ", Marker1, " on the endpoint ", Endpoint)) 
    TP<-Output_Biomarker$PredictionStat$tp; TN<-Output_Biomarker$PredictionStat$tn; FP<-Output_Biomarker$PredictionStat$fp; FN<-Output_Biomarker$PredictionStat$fn
    Sensitivity<-TP/sum(TP+FN) 
    Specificity<-TN/sum(FP+TN) 
    Prevalence<-seq(0,1,by=0.01)
    PPV<- (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) )
    NPV<- (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) )
    # PPV and NPV data for plot
    PPV_NPV_Dat<-data.frame(Prevalence=c(Prevalence,Prevalence),
                           Type=rep(c("PPV","NPV"), each =length(Prevalence)),
                           Val= c(PPV, NPV))
    PPVNPVPlot<-ggplot(PPV_NPV_Dat, aes(x=Prevalence*100, y= Val, color=Type)) +
                        geom_line(lwd=1.5) +  
                        theme_bw()   +
                        xlab("Prevalence Rate (%)") +
                        ylab("Predictive Value (%)") +
                        scale_x_continuous(breaks=seq(from=0, to=100, by=5))  +
                        scale_y_continuous(breaks=seq(from=0, to=100, by=5))+
                            theme(axis.text.y=element_text(size=18),axis.title=element_text(size=18),
                                      plot.title = element_text(hjust = 0.5,size=16),legend.text=element_text(size=16),legend.title=element_text(size=16),
                                      plot.subtitle=element_text(size=18, hjust=0.5, face="italic", color="black"),
                                      axis.text.x = element_text( size=18)) #+ stat_compare_means(method = "t.test")
  
   print(PPVNPVPlot)
   
   
     ###for table Predictive values of bio-marker panels for their intended use in populations with varying prevalence of disease phenotype for Marker 1
  TP<-Output_Biomarker$PredictionStat$tp; TN<-Output_Biomarker$PredictionStat$tn; FP<-Output_Biomarker$PredictionStat$fp; FN<-Output_Biomarker$PredictionStat$fn
  Sensitivity<-TP/sum(TP+FN) 
  Specificity<-TN/sum(FP+TN) 
   Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
                           PPV=PPV,
                           NPV=NPV,
                           Val=paste0(PPV,"%/",NPV,"%"))
   
   rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker1," on endpoint ", Endpoint,".csv"))
   
   
      
  ###for table Predictive values of bio-marker panels for their intended use in populations with varying prevalence of disease phenotype for Marker 2
   #  TP<-Output_Candidate$PredictionStat$tp; TN<-Output_Candidate$PredictionStat$tn; FP<-Output_Candidate$PredictionStat$fp; FN<-Output_Candidate$PredictionStat$fn
   #  Sensitivity<-TP/sum(TP+FN) 
   #  Specificity<-TN/sum(FP+TN) 
   # Prevalence=c(0.01, 0.05, 0.10, 0.20, 0.50, 0.75, 0.90)
   # PPV<- round( (Sensitivity * Prevalence)*100 / ( Sensitivity * Prevalence + (1-Specificity)*(1-Prevalence) ),2)
   # NPV<- round( (Specificity * (1-Prevalence))*100/ ( (1-Sensitivity) * Prevalence + Specificity*(1-Prevalence) ),2)
   # Tab_PPV_NPV<-data.frame(Prevalence=Prevalence,
   #                         PPV=PPV,
   #                         NPV=NPV,
   #                         Val=paste0(PPV,"%/",NPV,"%"))
   # 
   # rownames( Tab_PPV_NPV)=paste("Prevalence=", Prevalence)
   # write.csv(t(Tab_PPV_NPV),file=paste0("C:\\Users\\Yongfang.Lu\\OneDrive - Cytel\\Desktop\\FNIH\\Development\\Tables\\PPV and NPV of " ,Marker2," on endpoint ", Endpoint,".csv"))


}



```
<br>

## Table 14.2.4.7 Comparison of the diagnostic performance of Pro-C4 versus FIB-4   
<br>
 

```{r RPOC4vsFIB-4,echo=FALSE,results='asis',eval=FALSE}


Marker1="Pro-C4" # bio-marker 
Marker2="FIB-4" #candidate marker
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 


Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.7 Comparison of the diagnostic performance of Pro-C4 versus FIB-4")

Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>





## Table 14.2.4.8 Comparison of the diagnostic performance of Pro-C5 versus FIB-4   
<br>
 

```{r RPOC5vsFIB-4,echo=FALSE,results='asis',eval=FALSE}


Marker1="Pro-C5" # bio-marker 
Marker2="FIB-4" #candidate marker
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 


Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.8 Comparison of the diagnostic performance of Pro-C5 versus FIB-4")

Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>





## Table 14.2.4.9 Comparison of the diagnostic performance of Pro-C6 versus FIB-4   
<br>
 

```{r RPOC6vsFIB-4,echo=FALSE,results='asis',eval=FALSE}


Marker1="Pro-C6" # bio-marker 
Marker2="FIB-4" #candidate marker
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 


Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.9 Comparison of the diagnostic performance of Pro-C6 versus FIB-4")

Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>





## Table 14.2.4.10 Comparison of the diagnostic performance of ADAPT versus FIB-4   
<br>
 

```{r ADAPTvsFIB-4,echo=FALSE,results='asis',eval=FALSE}


Marker1="ADAPT" # bio-marker 
Marker2="FIB-4" #candidate marker
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 


Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.10 Comparison of the diagnostic performance of ADAPT versus FIB-4")

Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>