---
title: "FNIH Project"
author: "Yongfang (Modified by Souvik to add CI)"
date: "06/16/2021"
output:
  word_document:
    fig_width: 16
    fig_height: 10
    fig_caption: yes
    highlight: pygments
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}

library(knitr)
knitr::opts_chunk$set(echo=FALSE, cache=FALSE, eval=TRUE, warning=FALSE, message=FALSE,  fig.align = "center")

```


# Further formating is needed after kint the docuemnt
# 1: replace ** with whitespace
# 2: merge row of "Candidate Biomarker classification at the optimal cut-point"
# 3: merge row of "Performance Parameters at the optimal cut-point"
# 4: CI is calcuated as AUROC + (-1,+1)*1.96*SE(AUROC)


```{r loading R packages and source code , echo=FALSE}

rm(list=ls())
setwd("S:\\Clients\\FNIH\\R\\Development\\Code\\modifications")
DIR_FILES <- "S:\\Clients\\FNIH\\R\\Raw_Data\\"

library(openxlsx)
library(readxl)
library(stringr)
library(cutpointr)
library(dplyr)
library(pROC)
List<-c("SUBJID","ageyrs","platelet","Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis","NASH","NAS","At_Risk_NASH")
List_Endpoint<-List[-c(1:3)]
Def_Endpoint<-read.csv("S:\\Clients\\FNIH\\R\\Development\\Code\\FNIH_Endpoint_Definition.csv")


source("S:\\Clients\\FNIH\\R\\Development\\Code\\modifications\\Table_Fun2_Space_modified.R")
source("S:\\Clients\\FNIH\\R\\Development\\Code\\modifications\\Table_Fun_ComparsionCandiatevsBiomarkers_modified.R")


```


```{r For loading data, message=FALSE,warning=FALSE, results="markup"}

#####################################################################################
####################### #loading data and data handling ############################
#####################################################################################

Siemens<- read.csv(paste0(DIR_FILES,"Nimble_Siemens_24FEB2021.csv"))
Nordic<-  read.csv(paste0(DIR_FILES,"Nimble_Nordic_16APR2021.csv"))
Labcorp<- read_excel(paste0(DIR_FILES,"NIMBLE_labcorp_18Mar2021.xls"));Labcorp<-Labcorp[-(7453:7455),];Labcorp$Result<-as.numeric(as.character(Labcorp$RESULT))
MetaDat<- read_excel(paste0(DIR_FILES,"nimble_metadata_28mar21.xlsx"))
CRNDat<- read_excel(paste0(DIR_FILES,"nimble_owl_clinds_7apr21.xlsx"),sheet = "Data")
GenfitDat<- read.csv(paste0(DIR_FILES,"Nimble_Genfit_19072021.csv"))
OWLDat<-read.csv(paste0(DIR_FILES,"NIMBLE_OWLiver Panels_Results.csv"))
FibrometerDat1<-read.csv(paste0(DIR_FILES,"fibrometer_LSM_CAP_Agile_FAST_FMVCTE.csv"))
FibrometerDat2<- read.csv(paste0(DIR_FILES,"fibrometer_results_V3G_NAFLD_CirrhoMeter_p.csv"))

# caculating FIB-4
#FIB4<-Age (years)×AST (U/L)/[PLT(109/L)×ALT1/2 (U/L)].  

#processing data
# why lapcrop list patient names twice, keep one is enough-> YES!!!
PATIENT_NAME<-do.call("rbind",strsplit(Labcorp$`PATIENT NAME`, "        "))
# sum(PATIENT_NAME[,1]==PATIENT_NAME[,2])==nrow(PATIENT_NAME)
# Labcorp$`PATIENT NAME`<-PATIENT_NAME[,1]
# unique(Labcorp$TEST_ORD_NAME) # 7 unque parameters from Labcorp data
# # [1] "Protein, Total"       "Albumin"              "Bilirubin, Total"     "Bilirubin, Direct"    "Alkaline Phosphatase"
# # [6] "AST (SGOT)"           "ALT (SGPT)"
# 
# unique(Nordic$LBTESTCD) # 6 unique parameters from Nordic data
# #[1] C3M   C4M   PROC3 PROC4 PROC5 PROC6
# 
# unique(Siemens$LBTESTCD) # Siemen data holds the ELF_TEST reslt

# unique(GenfitDat$LBTESTCD) 
# "A2M"   "HBA1C" "NIS4"  "NISX" 

### check the correct subject ID to use in order to merge data
Nordic$SUBJID<-do.call("rbind",strsplit(as.character(Nordic$BARCODE), "LS"))[,1]
Nordic$SUBJID<-do.call("rbind",strsplit(Nordic$SUBJID, "N"))[,2]

Labcorp$SUBJID<-do.call("rbind",strsplit(as.character(Labcorp$`PATIENT NAME`), "L"))[,1]
Labcorp$SUBJID<-do.call("rbind",strsplit(Labcorp$SUBJID, "N"))[,2]

Siemens$SUBJID<-do.call("rbind",strsplit(as.character(Siemens$BARCODE), "LS"))[,1]
Siemens$SUBJID<-do.call("rbind",strsplit(Siemens$SUBJID, "N"))[,2]

#CRNDat$SUBJID<-do.call("rbind",strsplit(as.character(CRNDat$current_label), "LS"))[,1]
CRNDat$SUBJID<-do.call("rbind",strsplit(CRNDat$subjid, "N"))[,2]

GenfitDat$SUBJID<-do.call("rbind",strsplit(as.character(GenfitDat$BARCODE), "LS"))[,1]
GenfitDat$SUBJID<-do.call("rbind",strsplit(GenfitDat$SUBJID, "N"))[,2]



OWLDat$SUBJID<-do.call("rbind",strsplit(as.character(OWLDat$SAMPLE.ID), "LS"))[,1]
OWLDat$SUBJID<-do.call("rbind",strsplit(OWLDat$SUBJID, "N"))[,2]

FibrometerDat1$SUBJID<-do.call("rbind",strsplit(as.character(FibrometerDat1$SUBJID), "N"))[,2]
FibrometerDat2$SUBJID<-do.call("rbind",strsplit(as.character(FibrometerDat2$SUBJID), "N"))[,2]

MetaDat$SUBJID<-MetaDat$nash

# #check how many unique subjects in each data
# length(unique(Siemens$SUBJID))
# length(unique(Labcorp$SUBJID))
# length(unique(Nordic$SUBJID))
# length(unique(MetaDat$SUBJID))
# 
# sum(unique(Nordic$SUBJID) %in% unique(Siemens$SUBJID))
# sum(unique(Nordic$SUBJID) %in% unique(Labcorp$SUBJID))
# sum(unique(Labcorp$SUBJID) %in% unique(Siemens$SUBJID))
# sum(unique(MetaDat$SUBJID) %in% unique(Siemens$SUBJID))


#get the endpoints ready and handling the data
MetaDat$Fibrosis <-if_else(MetaDat$fibrosisn>=2,1,0)
MetaDat$Advanced_Fibrosis <-if_else(MetaDat$fibrosisn>=3,1,0)
MetaDat$Cirrhosis<-if_else(MetaDat$fibrosisn>=4,1,0)
MetaDat$Fibrosis_Excluding_Cirrhosis<-if_else(MetaDat$fibrosisn>=2,1,0); 
MetaDat$Fibrosis_Excluding_Cirrhosis[MetaDat$Cirrhosis==1]<-NA # this will be used to exclude subjects who are cirrhosis
MetaDat$NASH<-if_else(MetaDat$anynash==1,1,0)
MetaDat$NAS<-if_else(MetaDat$nas>=4,1,0)
MetaDat$At_Risk_NASH<-if_else( (MetaDat$NASH==1 & MetaDat$NAS==1 & MetaDat$Fibrosis==1),1,0)



Siemens$ELF<-Siemens$LBORRES

PROC3<-Nordic[Nordic$LBTEST=="Pro-C3",]
PROC3$'Pro-C3'<-PROC3$LBORRES
PROC3<-PROC3[,c("SUBJID","Pro-C3")]


PROC4<-Nordic[Nordic$LBTEST=="Pro-C4",]
PROC4$'Pro-C4'<-PROC4$LBORRES
PROC4<-PROC4[,c("SUBJID","Pro-C4")]


PROC5<-Nordic[Nordic$LBTEST=="Pro-C5",]
PROC5$'Pro-C5'<-PROC5$LBORRES
PROC5<-PROC5[,c("SUBJID","Pro-C5")]


PROC6<-Nordic[Nordic$LBTEST=="Pro-C6",]
PROC6$'Pro-C6'<-PROC6$LBORRES
PROC6<-PROC6[,c("SUBJID","Pro-C6")]

ALT<-Labcorp[Labcorp$TEST_ORD_NAME=="ALT (SGPT)",]
ALT$ALT<-ALT$Result
ALT<-merge(ALT, CRNDat[,c("SUBJID","alt")],all=TRUE)
ALT$ALT[is.na(ALT$ALT)]<-ALT$alt[is.na(ALT$ALT)]
ALT<-ALT[,c("SUBJID","ALT")]

AST<-Labcorp[Labcorp$TEST_ORD_NAME=="AST (SGOT)",]
AST$AST<-AST$Result
AST<-merge(AST, CRNDat[,c("SUBJID","ast")],all=TRUE)
AST$AST[is.na(AST$AST)]<-AST$ast[is.na(AST$AST)]
AST<-AST[,c("SUBJID","AST")]

NIS4<-GenfitDat[GenfitDat$LBTESTCD=="NIS4",]
NIS4$NIS4<-NIS4$LBORRES
NIS4<-NIS4[,c("SUBJID","NIS4")]

OWLDat$OWL<-OWLDat$DIGANOSIS
OWL<-OWLDat[,c("SUBJID","OWL")]

#Agile4	Agile3Plus	FAST	FMVCTE	FMVCTE_light and FM3G V - FibrosisScore	CirrhosisScore	NAFLD - FibrosisScore
Agile4<-FibrometerDat1[,c("SUBJID","Agile4")]
Agile3Plus<-FibrometerDat1[,c("SUBJID","Agile3Plus")]
FAST<-FibrometerDat1[,c("SUBJID","FAST")]
FMVCTE<-FibrometerDat1[,c("SUBJID","FMVCTE")]
FMVCTE_light<-FibrometerDat1[,c("SUBJID","FMVCTE_light")]

NAFLD<-FibrometerDat2[,c("SUBJID","NAFLD...FibrosisScore")]; colnames(NAFLD)<-c("SUBJID","NAFLD")
CirrhosisScore<-FibrometerDat2[,c("SUBJID","CirrhosisScore")]
FM3GV<-FibrometerDat2[,c("SUBJID","FM3G.V...FibrosisScore")]; colnames(FM3GV)<-c("SUBJID","FM3GV")

#####################################################################################
################### creating the dataset ready for analysis #####################
#####################################################################################
Dat_ELF<-merge(Siemens[,c("SUBJID","LBTESTCD","ELF")], MetaDat[,List],by="SUBJID")
saveRDS(Dat_ELF,file="Dat_ELF.rds")

Dat_PROC3<-merge(PROC3, MetaDat[,List],by="SUBJID")
saveRDS(Dat_PROC3,file="Dat_PROC3.rds")


Dat_NIS4<-merge(NIS4, MetaDat[,List],by="SUBJID")
saveRDS(Dat_NIS4,file="Dat_NIS4.rds")



Dat_All<-merge(Siemens[,c("SUBJID","ELF")], MetaDat[,List],by="SUBJID")
Dat_All<-merge(PROC3,Dat_All,by="SUBJID")
Dat_All<-merge(PROC4,Dat_All,by="SUBJID")
Dat_All<-merge(PROC5,Dat_All,by="SUBJID")
Dat_All<-merge(PROC6,Dat_All,by="SUBJID")
Dat_All<-merge(AST,Dat_All,by="SUBJID")
Dat_All<-merge(ALT,Dat_All,by="SUBJID")
Dat_All<-merge(NIS4,Dat_All,by="SUBJID")
Dat_All<-merge(OWL,Dat_All,by="SUBJID")
Dat_All<-merge(Agile4,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(Agile3Plus,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(FAST,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(FMVCTE,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(FMVCTE_light,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(NAFLD,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(CirrhosisScore,Dat_All,by="SUBJID",all.y = TRUE)
Dat_All<-merge(FM3GV,Dat_All,by="SUBJID",all.y = TRUE)

Dat_All$AGE<-floor(Dat_All$ageyrs)
Dat_All$'FIB-4'<-(Dat_All$AGE*Dat_All$AST)/(Dat_All$platelet *sqrt(Dat_All$ALT))

saveRDS(Dat_All,file="Dat_All.rds")


```
<br>
<br>

```{r For self-defined functions}


CutpointAnalysis<-function(Dat, Marker, Endpoint, Def_Endpoint){
  
  #only keep complete records
  Data<-Dat[complete.cases(Dat[,c(Marker,Endpoint)]),]
  
  #find optimum cutpoint
  opt_cut <- cutpointr(x=Data[,Marker],
                    class=Data[,Endpoint],
                    method =maximize_metric, 
                    metric = youden)
  
  # caculating P value
  AUC<-opt_cut["AUC"]$AUC
  a<- qnorm(AUC, mean=0, sd=1)*1.414
  n2=sum(Data[,Endpoint]==1)
  n1=sum(Data[,Endpoint]==0)
  Var_AUC<-( 0.0099*exp((-0.5)*a^2) )*( (5*a^2+8)/n2 + (a^2+8)/n1 ) 
  SE_AUC<-sqrt(Var_AUC)
  z.test<-(AUC-0.5)/SE_AUC
  Pvalue<- (1-pnorm(abs(z.test),mean=0,sd=1)) #this is 1-side test
  ci <- AUC +c(-1,1)*1.96*SE_AUC
  ci_format<- paste("[",round(ci[1],3),",",round(ci[2],3), "]")
 
  FIT=list()
  FIT[["Biomarker"]]<-Data[,Marker];
  FIT[["Endpoint"]]<-Data[,Endpoint];
  FIT[["AUCROC"]]<-opt_cut["AUC"]$AUC
  FIT[["Youden_Index"]]<-opt_cut["youden"]$youden
  FIT[["PredictionStat"]]<-summary(opt_cut)$confusion_matrix[[1]][1,c("tp", "fp","tn","fn")]
  FIT[["Optimal_cutpoint"]]<-round(opt_cut["optimal_cutpoint"]$optimal_cutpoint,1)
  FIT[["Optimal_cutpoint_direction"]]<-opt_cut["direction"]$direction
  FIT[["Pvalue"]]<-Pvalue
  FIT[["SE_AUCROC"]]<-SE_AUC
  FIT[["CI"]]<-ci_format
  FIT[["Biomarker_name"]]<-Marker
  FIT[["Endpoint_name"]]<-Endpoint
  FIT[["Endpoint_pos_var"]]<-Def_Endpoint$Positive[Def_Endpoint$Endpoint.variables==Endpoint]
  FIT[["Endpoint_neg_var"]]<-Def_Endpoint$Negative[Def_Endpoint$Endpoint.variables==Endpoint]
  
  return(FIT)
  
# Dat=Dat; Marker=Marker;Endpoint=Endpoint; Def_Endpoint =Def_Endpoint
# 
# #only keep complete records
# Data<-Dat[complete.cases(Dat[,c(Marker,Endpoint)]),]
#   
# #find optimum cutpoint
# opt_cut2 <- cutpointr(x=Data[,Marker],
#                     class=Data[,Endpoint],
#                     method =maximize_metric, 
#                     metric = youden,
#                     boot_runs = 10000)
#   
# AUCROC_Boot<- opt_cut2$boot[[1]]["AUC_b"]$AUC_b
# 
# 1-sum(AUCROC_Boot>=0.5)/length(AUCROC_Boot)
}


```
<br>
<br>

\newpage
# Chapter II: Diagnostic Performance Tables by Biomarkers
<br>
<br>



## Table 14.2.2.1 Diagnostic performance of candidate biomarker ELF  
<br>
 

```{r ELF,echo=FALSE,results='asis',eval=TRUE}


Dat=Dat_All;
Marker="ELF" 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")



for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]

Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.2.1 Diagnostic performance of ELF")

Table<-Table_Fun(FIT=Output)
print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))


}



```
<br>


## Table 14.2.2.2 Diagnostic performance of candidate Fibrometer biomarkers
<br>
 

```{r FibrosisScore,echo=FALSE,results='asis',eval=TRUE}


Dat=Dat_All;
#Marker_list<-c("FM3GV", "CirrhosisScore", "NAFLD")
Marker_list<-c("FM3GV", "CirrhosisScore", "NAFLD", "FMVCTE_light", "FMVCTE", "FAST", "Agile3Plus", "Agile4")
 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")

for(i in 1:length(Marker_list)){
  
    Marker<-Marker_list[i]
    
    for(j in 1:length(List_Endpoint_update)){
      
    Endpoint<-List_Endpoint_update[j]
    
    Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    
    cat(paste0("Table 14.2.2.2.",i, " Diagnostic performance of ", Marker))
    
    Table<-Table_Fun(FIT=Output)
    print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
    
    Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
    Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
      
    cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
    cat(paste("  ","  ","  ",sep="\n"))
    
    
    }
  }



```
<br>

## Table 14.2.2.3 Diagnostic performance of candidate biomarker NIS4  
<br>
 

```{r NIS4,echo=FALSE,results='asis',eval=TRUE}


Dat=Dat_All;
Marker="NIS4" 
List_Endpoint_update<-c("NASH","NAS","At_Risk_NASH","Fibrosis","Advanced_Fibrosis","Cirrhosis")



for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]

Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.2.3 Diagnostic performance of NIS4")

Table<-Table_Fun(FIT=Output)
print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))


}



```
<br>


## Table 14.2.2.4 Diagnostic performance of candidate biomarker OWL  
<br>
 

```{r OWL,echo=FALSE,results='asis',eval=FALSE}


Dat=Dat_All;
Marker="OWL" 
List_Endpoint_update<-c("NASH","NAS")

for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]

Output<-CutpointAnalysis_Catalog(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.2.4 Diagnostic performance of OWL")

Table<-Table_Fun_Catalog(FIT=Output)
print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))


}



```
<br>


## Table 14.2.2.5 Diagnostic performance of candidate biomarker Pro-C3  
<br>
 

```{r PROC3,echo=FALSE,results='asis',eval=TRUE}


Dat=Dat_All;
Marker="Pro-C3" 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")

for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]

Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.2.5 Diagnostic performance of Pro-C3")

Table<-Table_Fun(FIT=Output)
print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))


}



```
<br>

## Table 14.2.2.6 Diagnostic performance of candidate biomarker Pro-C4  
<br>
 

```{r PROC4,echo=FALSE,results='asis',eval=TRUE}


Dat=Dat_All;
Marker="Pro-C4" 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")

for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]

Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.2.6 Diagnostic performance of Pro-C4")

Table<-Table_Fun(FIT=Output)
print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))


}



```
<br>


## Table 14.2.2.7 Diagnostic performance of candidate biomarker Pro-C5  
<br>
 

```{r PROC5,echo=FALSE,results='asis',eval=TRUE}


Dat=Dat_All;
Marker="Pro-C5" 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")

for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]

Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.2.7 Diagnostic performance of Pro-C5")

Table<-Table_Fun(FIT=Output)
print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))


}



```
<br>



## Table 14.2.2.8 Diagnostic performance of candidate biomarker Pro-C6  
<br>
 

```{r PROC6,echo=FALSE,results='asis',eval=TRUE}


Dat=Dat_All;
Marker="Pro-C6" 
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis")

for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]

Output<-CutpointAnalysis(Dat=Dat, Marker=Marker, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.2.8 Diagnostic performance of Pro-C6")

Table<-Table_Fun(FIT=Output)
print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat("[2] P-value for the 1-sided test that AUROC > 0.5.")
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))


}



```
<br>

# Chapter IV: Comparison of the diagnostic performance of candidate marker versus biomarker 

## Table 14.2.4.1 Comparison of the diagnostic performance of ELF versus FIB-4   
<br>
 

```{r ELFvsFIB-4,echo=FALSE,results='asis',eval=TRUE}

Marker1="ELF" # bio-marker 
Marker2="FIB-4" #candidate marker

List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 

Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.1 Comparison of the diagnostic performance of ELF versus FIB-4")

Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>



## Table 14.2.4.2 Comparison of the diagnostic performance of Fibrometer biomarkers versus FIB-4   
<br>
 

```{r FibrometervsFIB-4,echo=FALSE,results='asis',eval=TRUE}

Marker_list<-c("FM3GV", "CirrhosisScore", "NAFLD", "FMVCTE_light", "FMVCTE", "FAST", "Agile3Plus", "Agile4")
Marker2="FIB-4" #candidate marker

List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")

 for(i in 1:length(Marker_list)){
   
    Marker1<-Marker_list[i]
     
    for(j in 1:length(List_Endpoint_update)){
      
    Endpoint<-List_Endpoint_update[j]
    Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 
    
    Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
    
    cat(paste0("Table 14.2.4.2.",i," Comparison of the diagnostic performance of ", Marker1," versus FIB-4"))
    
    Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)
    
    print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("  ","  ","  ",sep="\n"))
    
    Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
    Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
      
    cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
    cat(paste("  ","  ","  ",sep="\n"))
    cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
    cat(paste("  ","  ","  ",sep="\n"))
    
    }
 }


```
<br>


## Table 14.2.4.3 Comparison of the diagnostic performance of NIS4 versus ALT   
<br>
 

```{r NIS4vsALT,echo=FALSE,results='asis',eval=TRUE}

Marker1="NIS4" # bio-marker 
Marker2="ALT" #candidate marker

List_Endpoint_update<-c("NASH","NAS")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 

Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.3 Comparison of the diagnostic performance of NIS4 versus ALT")

Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>


## Table 14.2.4.4 Comparison of the diagnostic performance of NIS4 versus FIB-4   
<br>
 

```{r NIS4vsFIB-4,echo=FALSE,results='asis',eval=TRUE}

Marker1="NIS4" # bio-marker 
Marker2="FIB-4" #candidate marker

List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 

Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.4 Comparison of the diagnostic performance of NIS4 versus FIB-4")

Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>

## Table 14.2.4.5 Comparison of the diagnostic performance of OWL versus ALT   
<br>
 

```{r OWLvsALT,echo=FALSE,results='asis',eval=FALSE}

Marker1="OWL" # bio-marker 
Marker2="ALT" #candidate marker

List_Endpoint_update<-c("NASH","NAS")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 

Output_Biomarker<-CutpointAnalysis_Catalog(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.5 Comparison of the diagnostic performance of NIS4 versus ALT")

Table<-Table_Fun_Comparison_Catalog(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>



## Table 14.2.4.6 Comparison of the diagnostic performance of Pro-C3 versus FIB-4   
<br>
 

```{r RPOC3vsFIB-4,echo=FALSE,results='asis',eval=TRUE}


Marker1="Pro-C3" # bio-marker 
Marker2="FIB-4" #candidate marker
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 


Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.6 Comparison of the diagnostic performance of Pro-C3 versus FIB-4")

Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>



## Table 14.2.4.7 Comparison of the diagnostic performance of Pro-C4 versus FIB-4   
<br>
 

```{r RPOC4vsFIB-4,echo=FALSE,results='asis',eval=TRUE}


Marker1="Pro-C4" # bio-marker 
Marker2="FIB-4" #candidate marker
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 


Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.7 Comparison of the diagnostic performance of Pro-C4 versus FIB-4")

Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>





## Table 14.2.4.8 Comparison of the diagnostic performance of Pro-C5 versus FIB-4   
<br>
 

```{r RPOC5vsFIB-4,echo=FALSE,results='asis',eval=TRUE}


Marker1="Pro-C5" # bio-marker 
Marker2="FIB-4" #candidate marker
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 


Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.8 Comparison of the diagnostic performance of Pro-C5 versus FIB-4")

Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>





## Table 14.2.4.9 Comparison of the diagnostic performance of Pro-C6 versus FIB-4   
<br>
 

```{r RPOC6vsFIB-4,echo=FALSE,results='asis',eval=TRUE}


Marker1="Pro-C6" # bio-marker 
Marker2="FIB-4" #candidate marker
List_Endpoint_update<-c("Fibrosis","Advanced_Fibrosis","Cirrhosis", "Fibrosis_Excluding_Cirrhosis")


for(i in 1:length(List_Endpoint_update)){
  
Endpoint<-List_Endpoint_update[i]
Dat<-Dat_All[complete.cases(Dat_All[,c(Marker1,Marker2,Endpoint)]),] #use only common subjects for comparison 


Output_Biomarker<-CutpointAnalysis(Dat=Dat, Marker=Marker1, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)
Output_Candidate<-CutpointAnalysis(Dat=Dat, Marker=Marker2, Endpoint=Endpoint, Def_Endpoint =Def_Endpoint)

cat("Table 14.2.4.9 Comparison of the diagnostic performance of Pro-C6 versus FIB-4")

Table<-Table_Fun_Comparison(FIT_Biomarker=Output_Biomarker, FIT_Candidate=Output_Candidate)

print(kable(Table,align="c",caption=paste0("Endpoint= ", Endpoint) ,row.names = NA))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("  ","  ","  ",sep="\n"))

Endpoint_pos_var<-Output_Biomarker[["Endpoint_pos_var"]] 
Endpoint_neg_var<-Output_Biomarker[["Endpoint_neg_var"]] 
  
cat(paste0("[1] Classification: positive = ",Endpoint_pos_var, " and negative = ", Endpoint_neg_var,"."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste0("[2] P-value for the 1-sided test that AUROC(",Marker1,") > AUCROC(",Marker2,")."))
cat(paste("  ","  ","  ",sep="\n"))
cat(paste("[3] Value of the candidate biomarker that gives the best classification."))
cat(paste("  ","  ","  ",sep="\n"))

}



```
<br>